{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-27 paper/tex/sections/introduction.tex
small changes from comments

Traditionally, investigations into detecting stellar-mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}. More recently, interest has grown in the detection of NS and BH binaries. Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars. In this paper we focus on making LISA predictions for double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).

>>>>

Traditionally, predictions about the detection of stellar-mass sources with LISA focus on double white dwarf (WDWD) binaries, as they are abundantly present in our galaxy and are expected to be the dominant source of stellar-mass binaries that are detectable by LISA \citep{Nelemans+2001,Ruiter+2010,Yu+2010,Nissanke+2012,Korol+2017,Lamberts+2018}. More recently, interest has grown in the detection of NS and BH binaries. Although they are more rare, LISA detections of these sources are potentially valuable for learning more about the evolution and endpoints of massive stars. In this paper we focus on making LISA predictions for double black hole binaries (BHBH), black hole neutron star binaries (BHNS) and double neutron star binaries (NSNS).

### 2021-08-27 paper/tex/sections/variations.tex
small changes from comments

\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here}

>>>>

\todo{Discuss $\alpha_{\rm CE}$ changes: It seems that alpha=1 is a sweet spot for BHBH and BHNS (they seem to follow the same trend) whilst NSNS has a very different pattern -- not really sure what's happening here. UPDATE: this is almost entirely a formation rate thing rather than a detection rate trend so we can focus on that}
